---
title: "Taking The Bible Literally"
author: "Daniel Baggett"
date: '2019-07-04'
categories: Bible
draft: yes
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
lastmod: '2019-07-04T14:07:18-04:00'
projects: []
slug: taking-the-bible-literally
subtitle: ''
summary: ''
tags: []
authors: []
---

```{r library chunk, echo=FALSE, include=FALSE}
library(tidyverse)
```

I normally begin my American History Survey courses by asking students to give me a one sentence rundown of a particular era in History. The responses are a great way for me to quickly gauge if the material is sinking in. 

The Great Depression?
Student: "FDR saved us from Hitler and the stock market." (I have a lot of work to do.)

Reconstruction?
Student: "It was an attempt at putting the United States back together after the worst break up imaginable." (I can work with this!)

The Reformation
Student: "Normal people were given access to the bible and chaos broke out." (Yes)

The last one-line sentence is difficult for 21st century American students to understand.  

The Reformation was *at least* a fight over the right to interpret. I was curious to see if the GSS survey contained any variables about the interpretation of the bible. 

I think the intention of the GSS "bible" variable was to ilicit general feelings about the bible. I found the second part of their question much more interesting. 

***
Which of these statements comes closest to describing your feelings about the Bible?  
A. The Bible is the actual word of God and is to be taken literally, **word for word**.
B. The Bible is the inspired word of God **but not everything in it should be taken literally, word for word**.
C. The Bible is an ancient book of fables, legends, history, and moral precepts recorded by men.

```{r}
serve_site()
```






