---
title: People are naming their children after Creed Bratton. 
author: Daniel Baggett
date: '2019-05-31'
slug: kramer-or-daenarys
categories:
  - R
tags:
  - Tidytuesday
subtitle: ''
summary: ''
authors: []
lastmod: '2019-05-31T17:17:05-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
draft: true
---



```{r library chunk, echo=FALSE, include=FALSE}
library(tidyverse)
library(babynames)
library(knitr)
library(stringr)
library(janitor)
```


If you've used the internet this year, you've probably seen a chart like this:

```{r Daenerys All, echo = FALSE}
Daenerys_all <- babynames %>% filter(name == "Daenerys" & sex == "F")
ggplot(Daenerys_all, aes(x = year, y = n, color = name)) + 
  geom_line(size = 1.0) +
  labs(title = "Sweetie, you are named after the Mother of Dragons") +
  ylab("Number of Children")
```

Yes. People are naming their children after characters from Game of Thrones. 


Working from the ever-popular [babynames dataset](https://www.kaggle.com/kaggle/us-baby-names), I wanted to see if people were naming their children after characters that are *truly* odd. 

Are people naming their children Seven [like George wanted to in Seinfeld?](https://www.youtube.com/watch?v=NRUdaWZ4FN0) What about [Beans from Even Stevens,](https://www.imdb.com/name/nm0493037/) or [Phoebe from Friends?](https://en.wikipedia.org/wiki/Phoebe_Buffay)



##Critera
1. Truly Odd  **< 100** uses per year before the show's debut.
2. Honorable Mentions - Barely missed the mark. 
3. Too weird for literally anyone.

***

###Honorable Mention Category
```{r honorable mentions, echo=FALSE}
honorable_mentions <- babynames %>% filter(name == "Phoebe" & sex == "F" | name == "Sheldon" & sex == "M" | name == "Rory" & sex == "F" | name == "Lorelei" & sex == "F", year >= 1950)

honorable_mentions_tot <- honorable_mentions %>% group_by(name) %>% 
  summarise(total = sum(n))

ggplot(honorable_mentions, aes(x = year, y = n, color = name)) + 
  geom_line(size = .9) +
  labs(title = "Honorable Mentions") +
  xlab("Year") +
  ylab("Children Named")
```

1. Lorelei, Gilmore Girls (2000 to 2007)
2. Phoebe, Friends (1994 to 2004)
3. Rory, Gilmore Girls (2000 to 2007)
4. Sheldon, Big Bang Theory (2007 to It Will Never End)

The Big Bang Theory's popularity spawned a prequel of a show inside of a show that is **still running.** I figured Sheldon would be a lot higher.

***

###Truly Odd Category. 
```{r Odd Names, echo=FALSE}
Odd_Names <- babynames %>% filter(year >= 1970, name == "Creed" & sex == "M" | name == "Gunther" & sex == "M" | name == "Kramer" & sex == "M" | name == "Seven" & sex == "M")
 
ggplot(Odd_Names, aes(x = year, y = n, color = name)) + 
                  geom_line(size = 1.0) +
                  labs(title = "Truly Odd Names from TV Shows") +
                  xlab("Year") +
                  ylab("Number of Children Named")
```

1. Creed, The Office (2005)
2. Gunther, Friends (1994 - 2004)
3. Kramer, Seinfeld (1989 - 1998)
4. Seven, Seinfeld (1989 - 1998)



Yes... That **Creed Bratton** line is accurate!
<br>
Yes... People are really naming their children "Seven" even though George was never able to use it himself.

To further prove the point, here is the average number of names, per year, adjusted for the show's time on television. 

```{r Per Year, echo = FALSE}
meanCreed <- babynames %>% filter(name == "Creed" & sex == "M", year >= 2005) %>% 
  group_by(name) %>% 
  summarize(mean = mean(n)) 

meanSeven <- babynames %>% filter(name == "Seven" & sex == "M", year >= 1989) %>% 
  group_by(name) %>% 
  summarize(mean = mean(n)) 

meanKramer <- babynames %>% filter(name == "Kramer" & sex == "M", year >= 1989 & year <= 1996) %>% 
  group_by(name) %>% 
  summarize(mean = mean(n)) 

meanGunther <- babynames %>% filter(name == "Gunther" & sex == "M", year >= 2005) %>% 
  group_by(name) %>% 
  summarize(mean = mean(n)) 

truly_odd_means <- rbind(meanGunther, meanKramer, meanSeven, meanCreed)

truly_odd_means %>% mutate(name = fct_reorder(name, mean)) %>% 
  ggplot(aes(name, mean, fill = name)) + 
  geom_col(width = .8) +
  coord_flip() +
  labs(title = "Average per year after show debut.") +
  ylab("Number of Children Given One of These Names Per Year") +
  xlab("Names")

```


Maybe Creed was a popular name sometime long ago and it is *just now* coming back into style?
```{r Bonus Creed, echo=FALSE}
Creed_All <- babynames %>% filter(name == "Creed" & sex == "M")
ggplot(Creed_All, aes(x = year, y = n)) + geom_line() + labs()
```
To be fair, Creed was on the rise before The Office debuted in 2005; however, It's safe to say that some were inspired by the character depicted on the show.  

###Too Weird for literally anyone. 
No one, and I mean no one, has named their child after [Beans](https://www.youtube.com/watch?v=NXOISYS5ubY&t=29s). When Shia LaBeouf made a movie of himself watching himself in all of the movies he has starred in, he cried [in only one](https://www.youtube.com/watch?v=NXOISYS5ubY&t=29s).




